DATA 621 Homework #3

### 2019-10-23 hw3/HW3.Rmd
Updated HW3.Rmd

```{r}
df <- read.csv('data/crime-training-data_modified.csv')
evaluation <- read.csv("data/crime-evaluation-data_modified.csv")
```

```{r}
set.seed(42)
train_index <- createDataPartition(df$target, p = .8, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

@@

```{r}
for (var in names(train)){
  if(var != "target"){
    plot_df <- train
    plot_df$y <- plot_df[,var]
    p <- ggplot(plot_df, aes(target, y, fill = factor(target))) +
      geom_boxplot() +
      theme_light() +
      ggtitle(var) +
      theme(legend.position = "none",
            axis.title.y = element_blank(),
            axis.title.x = element_blank(),
            axis.text.x = element_blank(),
            axis.ticks.x = element_blank())
    print(p)
  }
}
```

>>>>

```{r}
df <- read.csv('data/crime-training-data_modified.csv')
evaluation <- read.csv("data/crime-evaluation-data_modified.csv")
set.seed(42)
train_index <- createDataPartition(df$target, p = .8, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

@@

The following show the how predictors are distributed between the areas with crime rates higher than the median *blue) and below the median (red).

```{r}
for (var in names(train)){
  if(var != "target"){
    plot_df <- train
    plot_df$x <- plot_df[,var]
    p <- ggplot(plot_df, aes(x, color = factor(target))) +
      geom_density() +
      theme_light() +
      ggtitle(var) +
      scale_color_brewer(palette = "Set1") +
      theme(legend.position = "none",
            axis.title.y = element_blank(),
            axis.title.x = element_blank())
    print(p)
  }
}
```
